Empirical Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-01-19 written/paper.tex
minor written

\title{Expected Option Returns and the risk-free Rate in Crypto Asset Markets}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{7 January 2024}

@@

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., severe overpricings of at-the-money options. The effect holds after compensating for market crash insurance and transaction cost. 
We assess the deadeweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.

Evidence for leverage effect?

@@

@@

@@

\begin{table}[]
\begin{tabular}{lllll}
     & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\

@@

\end{tabular}

@@

\begin{equation}
C_t = e^{-r \tau} \mathbb{\sf{E}}^Q[\psi(S_T)] = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) f_t^Q(u) du
\end{equation}

where the PK \(K(\cdot)\) is defined as \(\frac{q(\cdot)}{p(\cdot)}\)
and for simplicity of notation we write \(q(\cdot)\) for
\(\frac{\partial Q}{\partial t}(\cdot)\) and drop the sequence \(r_t\).

\section{Nonparametric Estimation of State Price Densities}

\subsection{Derivation}

\subsection{Local Polynomial Estimation of the IV Surface}

Assume that the implied volatilites have some noise added (Huynh et al.
2002; Rookley 1997).

\begin{equation}
\sigma (M, \tau) = g(M, \tau) + \sigma^{*}(M, \tau)  \varepsilon
\end{equation}

with a standardized error random variable \(\varepsilon\), moneyness
\(M\), \(\tau\) and \(\varepsilon\) independent and
\(\sigma^{*}(M, \tau)\) being the scaling of the error term given \(M\)
and \(\tau\). Suppose \(g\) is smooth, i.e.~it can be approximated using
Taylor's Theorem.

Taylor expansion of \(g\) in a neighborhood of \((M_0, \tau_0)\):
\begin{equation}
\begin{aligned}
g(M, \tau) = g(M_0, \tau_0) +
\frac{\partial g}{\partial M}(M-M_0) + 
\frac{1}{2} \frac{\partial^2 g}{\partial M^2}(M-M_0)^2 + \\
\frac{\partial g}{\partial \tau}(\tau - \tau_0) + 
\frac{1}{2} \frac{\partial^2 g}{\partial \tau^2}(\tau - \tau_0)^2 + \\ 
\frac{\partial^2 g}{\partial M \partial \tau}(M-M_0)(\tau - \tau_0)
\end{aligned}
\end{equation}

The functional relationship between the IV surface \(\sigma\) and \(M\)
and \(\tau\) can now be approximated using a Weighted Least Squares
Estimator (WLSE), minimizing the objective function

\begin{equation}
\operatorname{arg}\, \underset{\beta}{\operatorname{min}}{(\sigma - X\beta)^\top W (\sigma - X\beta)}
\end{equation}

where
\(W = \text{diag}(\mathcal{K}_{h_m, h_\tau}(M_j - M_0, \tau_j - \tau_0))\)
for a Gaussian kernel \(\mathcal{K}\) with bandwidths \(h_m\) and
\(h_\tau\). \(\sigma\) is the \(n \times 1\) vector of observed implied
volatilities, \(\beta\) is the vector of the local polynomial
coefficients.

\[
X = 
\begin{pmatrix}
1 & (M_1 - M_0) & (M_1 - M_0)^2 & (\tau_1 - \tau_0) & (\tau_1 - \tau_0)^2 & (M_1 - M_0) (\tau_1 - \tau_0) \\
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \\
1 & (M_n - M_0) & (M_n - M_0)^2 & (\tau_n - \tau_0) & (\tau_n - \tau_0)^2 & (M_n - M_0) (\tau_n - \tau_0) \\
\end{pmatrix}
\]

The resulting WLSE is

\begin{equation}
\hat{\beta} = (X ^\top WX)^{-1}X ^\top W \sigma
\end{equation}

Following Härdle et al. (2014), a window of the last 500 daily returns
(based on \(\tau\)) is used to calculate a nonparametric Kernel Density
Estimator for the PD.\\
\href{https://quantinar.ro/course/103/statistics-of-financial-markets}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/quantinar_logo.png}}\,Chapter 24}

Breeden and Litzenberger (1978) derive SPDs using Arrow-Debreu prices
and Butterfly Spreads. Their paper was the cornerstone for the now
existing vast literature on estimation of SPDs. Without requiring a
parametric form for SPDs, Rookley (1997) who developed a nonparametric
estimation method. IV skews are estimated by decomposing the functional
relationship between IV, moneyness and time-to-maturity \(\tau\). In
this manner it is possible to derive the SPD at every point in a robust
way. Aı̈t-Sahalia et al. (2001) estimate PKs from S\&P500 options data
and the according return series in order to assess the efficiency of the
options market. Departures from SPD and PD are used to identify
inefficient pricing. They design a trading strategy, exploiting the
skewness and kurtosis of the densities. The strategy is shown to have a
high Sharpe Ratio. Grith et al. (2009) propose a systematic modeling
approach to study the evolution of PKs over time. With European DAX
data, a series of empirical PKs is estimated from 2003 until 2006. While
the risk-neutral density is inferred using Rookley's method, the PD is
estimated with a GARCH model. A common shape is identified and
deviations of the time varying EPKs are studied. The deviations between
individual PKs are described using a set of parameters for horizontal
and vertical shifts. The relationship between PKs and Arrow-Pratt
measure of Absolute Risk Aversion (ARA) give insight into investor's
risk aversion. In a related research, Härdle et al. (2014) derive
bootstrap-based confidence bands for nonparametrically estimated PKs.

Inverse Options, meaning options settled in kind of the underlying, are
dominant in the crypto world. Settlement of BTC options in terms of BTC
changes the payoff function of the option from \(\max(S_T - K; 0)\) to
\(\max(\frac{S_T - K}{S_T}; 0)\) and thus changes the contract's net
present value. Alexander and Imeraj (2021) adjust Black-Scholes prices
and hedge ratios to inverse options. However, it is argued that traders
are erroneously applying vanilla Black-Scholes valuation instead of the
corrected prices - perhaps because of being unaware of the concept. We
have decided to use with the standard, non-inverse Black Scholes pricing
for multiple reasons. Alexander and Imeraj (2021) argue that traders are
perhaps unaware of the difference. Since we are inferring investor
expectations, we figure that it is more appropriate to infer pricing
kernels under the same Black Scholes prices that the investors use.
Additionally, it is likely that many traders actually hedge their
overall Bitcoin exposure. This would negate the ``inverse'' part of the
option. Furthermore, reviewing the differences in pricing compared to
the adjusted prices, we find that the difference is small in the absence
of extreme moves in the underlying. This was not the case in the time
period under consideration.

Hou et al. (2020) price BTC options under an SVCJ model. Their results
emphasize the tail risk introduced by jumps in the underlying. Jumps in
particular introduce market incompleteness, but anonymity of
transactions may be relevant as well. Chen and Vinogradov (2021) derive
PKs and the impact of market incompleteness on risk premia. They state
that a key property of cryptocurrency valuation is the user's anonymity
(or pseudonymity), which is simultaneously the source of value and
incompleteness in the respective market. They argue that hedging an
anonymous transaction would require an identity disclosure. This
contradiction may introduce an effectively unhedgeable event.

@@

\section{Volatility}

In accordance with Masset (2011) and Eraker (2021), the list of
well-established stylised facts on volatility in traditional markets
include horizontal dependence of volatility, leverage effect, the
volatility premium and extreme events. Horizontal dependence of
volatility describes the tendency of local volatility clusters and the
tendence to mean-reversion. Both properties can be observed in the 7 day
rolling volatility. Sudden spikes in realized volatility form clusters
and are often followed by similar drops. The leverage effect can be
measured as a negative correlation between returns and volatility.
Phases of negative returns coincide with high volatility and vice versa.
The Pearson correlation between the underlying and realized volatility
is -12.59\%. The Pearson correlation between the underlying and the bid
(ask) IV is -16.11\% (-13.05\%). Due to the low absolute values of
correlation, the existence of a leverage effect is unlikely. However,
the sign matches the direction of a leverage effect. Considering the
large share of retailers with easy access to leverage, the lack of
significance is a surprising result. It is well known that, in general,
the IV exceeds the unconditional annualized standard deviation. This is
displayed in Figure \ref{fig: iv_comparison}. The difference between the
implied and realized volatility is commonly referred to as volatility
premium. The mean 7 day rolling volatility is 70.96\%, whereas the mean
IV at the bid and ask are 85.28\% and 93.57\%. Spikes in realized
volatility rarely exceed the ask of the IV. Consequently, the volatility
premium is shown to be substantial throughout the regarded time period.
Fat-tail events are priced in due to the classic volatility skew. This
is depicted in Figure \ref{fig: emp_ivsmile}, the empirical volatility
skew.

Since the data are high frequency order book snapshots with substantial
bid-ask spreads, we must address the issue of Market Microstructure
Noise (MMN). A simple estimate of realized volatility would increase
with our sample due to order competition within the spread. We resolve
the issue of MMN in our calculation of realized volatility by taking the
arithmetic mean after aggregating the implied volatility of bids and
asks on a daily base. Therefore the frequency is matching the underlying
BTC index. The formula for annualized, realized volatility of price
\(p\) over a window of \(w\) days is

\begin{equation}
\sigma_w = \sqrt{\frac{1}{w}\sum_{t=1}^w{(\log{p_t} - \log{p_{t-1})}^2}} \sqrt{\frac{365}{w}}
\end{equation}

Annualization is based on 365 days since Bitcoin options are traded
continuously on Deribit.

The term structure itself is easier to assess when regarding ATM-options
in a series of dates (Figure 6). ATM-options are defined as those
options, whose moneyness falls in the interval \([0.9, 1.1]\). A typical
term structure of the Bitcoin options reveals a high level of implied
volatility for shorted-dated options. For options with a
time-to-maturity of three days or more, implied volatility drops sharply
compared to the initial level. Naturally, IV is increasing with
time-to-maturity.

\begin{center}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/iv_comparison_up.png}
\caption[Implied Volatiliy vs. Realized Volatility on Deribit]%
{Implied volatility vs. realized volatility. Realized volatility is annualized and regarded in a 7 day window.
IV is calculated as the average of observed orderbooks at the bid and ask. Described data filters apply. {\color{blue} Ask IV}, {\color{green} Bid IV}, {\color{red} 7 Day Rolling Volatility}.}
\label{fig: iv_comparison}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Volatility}
\end{figure}
\end{center}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-05-23.png}
\caption[Empirical Volatility Surface]{Volatility Skew shown in the empirical Volatility Surface on 2021-05-23}
\label{fig: emp_ivsmile}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-09-08.png}
\caption[Empirical Volatility Surface 2]{Volatility Skew shown in a calmer period on 2021-09-08}
\label{fig: emp_ivsmile2}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola_plots.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,IV Smile}
\end{figure}
\end{centering}

\begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-010.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-020.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-030.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-040.08.png}

\end{minipage}
\begin{minipage}{0.5\textwidth}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-050.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-060.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-070.08.png}
        \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-080.08.png}

\end{minipage}
    \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}

\pagebreak
\newpage
\section{Empirical Pricing Kernels}

Instruments are grouped by time-to-maturity in order to summarize the
findings. All instruments with less than one week to maturity are
classified as having less than one, between one and two, between two and
three, between three and four and between five and eight weeks to
maturity. We typically observe U-shaped PKs for short-term maturities.
In a similar fashion to the oil market, investors perceive short-term
price changes in any direction as undesirable and prefer to hedge their
risk (Christoffersen et al. 2021). For short-dated instruemnts, option
writers are asking for substantial risk premia in order to reflect
unhedgeable risks, such as jumps in the underlying (Hou et al. 2020).

We find a differnet shape for longer-dated instruments. Typically, PKs
in traditional markets are monotonically decreasing. This results from
human risk aversion; investors are willing to insure themselves against
losses and have a preference for smooth consumption curves. However, PKs
outside of index options markets are not well studied (Cuesdeanu and
Jackwerth 2018). Grith et al. (2009) compartmentalize a pricing kernel
in two segments around a possible breakpoint. Testing an unrestricted
model against GMM estimates of the restricted one, they reject
monotonicity of the empirical PK in four out of five cases (performing a
D-test). The phenomenon of having a decreasing slope, although with
locally increasing sections in empirical PKs is called the pricing
kernel puzzle. We observe a similar behavior and extend the existing
literature on the pricing kernel puzzle to a new asset class.

Since the empirical PKs for short-dated instruments are U-shaped, we
figure that investors are willing to pay a high risk premium in order to
insure immediate price risks. With an increasing maturity of the
instrument, the shape of the empirical PK resembles a ``W'' or
``tilde''. This corresponds to a a lesser willingness to pay a risk
premium.\\
The dynamic of the empirical PKs also reveals the existence of a
time-varying risk premium in BTC markets. The observed PK shapes are
closely aligned with the results reported in Cuesdeanu and Jackwerth
(2018). However, their object of study are traditional markets, such as
major indices which are highly correlated with aggregate wealth. We
conclude that, due to the similarities of the empirical PKs, BTC is well
on its way to becoming an established asset class. It may prove to be
much rather a store of value than it is currently given credit for.

Apart from the discussion of results, deviations between PD and SPD can
be interpreted as trading opportunities. (Blaskowitz et al. 2004) design
and evaluate trading strategies based on deviations between PD and SPD.
Estimated PKs could be used by traders employing so-called Skewness or
Kurtosis trades. Nevertheless, traders must recognize the hidden cost of
employing such strategies in terms of substantial hedging cost, e.g.~in
the form of volatility and large spreads.

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=0.png}
\caption[Empirical Pricing Kernel - 0 Weeks to Expiration]{Pricing Kernels with less than one Week to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=1.png}
\caption[Empirical Pricing Kernel - 1 Week to Expiration]{Empirical Pricing Kernel - 1 Week to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=2.png}
\caption[Empirical Pricing Kernel - 2 Weeks to Expiration]{Empirical Pricing Kernel - 2 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=3.png}
\caption[Empirical Pricing Kernel - 3 Weeks to Expiration]{Empirical Pricing Kernel - 3 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=4.png}
\caption[Empirical Pricing Kernel - 4 Weeks to Expiration]{Empirical Pricing Kernel - 4 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=8.png}
\caption[Empirical Pricing Kernel - 5-8 Weeks to Expiration]{Empirical Pricing Kernel - 5-8 Weeks to Expiration}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
\end{figure}
\end{centering}

\section{Bootstrap-based Confidence Bands}

Having computed a large set of empirical PKs with varying maturities, it
should be ensured that the observed features are not mere artefacts. A
useful tool to assess the validity of our estimated PKs are
bootstrap-based confidence bands. Following the derivation of Härdle et
al. (2014), confidence bands at any confidence level can be derived via
the ``wild bootstrap method''. Figure
\ref{fig:Bootstrapped Confidence Bands - 2 Days} until Figure
\ref{fig:Bootstrapped Confidence Bands - 84 Days} are depicted
exemplarily for the whole set. Confidence bands are tighter around the
PKs when time to maturity increases. PKs are also flatter with growing
time to maturity.

The concept of bootstrapping PK can be introduced by linearization of
the PK. Stochastic deviation of the PK can be linearised into a
stochastic part, containing the estimator of the SPD and a deterministic
part containing the expectation of the physical density. Convergence of
both parts can be proven separately.

\[
\widehat{K}(x) = \frac{\widehat{q}(x)}{\widehat{p}(x)} 
\]

\[
\begin{aligned}
\underset{x \in E}{\operatorname{sup}} \lvert \widehat{K}(x) - K(x) \rvert = \underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} - \frac{\widehat{p}(x) - p(x)}{p(x)} * \frac{q(x)}{p(x)} - \frac{\{\widehat{q}(x) - q(x)\} \{\widehat{p}(x) - p(x)\} }{p^2(x)} \rvert  \\
+ {\scriptstyle \mathcal{O}_p}[\operatorname{max}((n_p h_{n_p}/\log)^{-1/2} + h^2_{np},h_{n_q}^{-2} \{ n_q h_{n_q} / \log{n_q} \}^{-1/2} + h^2_{n_q})]
\end{aligned}
\]

Consider the leading term of \[
\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} \rvert
\]

Resample data from the smoothed bivariate distribution of strike and
moneyness (X,Y)

\[
{\widehat{f}(x,y)} = \frac{\widehat{\sigma_X}}{n_q h^2_{n_q}\widehat{\sigma_Y}} 
\Sigma_{i=1}^{n_q} K
\{ 
\frac{X_i - x}{h_{n_q}}, 
\frac{(Y_i - y)\widehat{\sigma_X}}{h_{n_q}\widehat{\sigma_Y}}
\}
\]

Using the resampled data, calculate the bootstrap analogue

\[
\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}^*(x) - \widehat{q}(x)}{p(x)} \rvert
\]

where
\(\underset{x \in E}{\operatorname{sup}} \lvert\widehat{q}^*(x) - \widehat{q}(x) \rvert\)
converges to the Gumbel distribution at an unfortunately slow rate of
\(\frac{1}{\log n_q}\) (Hall 1991).

\begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0055.pdf}
    \captionof{figure}{2 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 2 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0192.pdf}
    \captionof{figure}{7 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 7 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0384.pdf}
    \captionof{figure}{14 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 14 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0575.pdf}
    \captionof{figure}{21 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 21 Days}

\end{minipage}
\begin{minipage}{0.5\textwidth}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0767.pdf}
    \captionof{figure}{28 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 28 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.1534.pdf}
        \captionof{figure}{56 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 56 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.2301.pdf}
        \captionof{figure}{84 Days to Maturity. \color{red}{Empirical Pricing Kernels} with \color{blue}{bootstrapped Confidence Bands} on 2021-12-31.}
    \href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
    \label{fig:Bootstrapped Confidence Bands - 84 Days}
\end{minipage}

Empirical PKs have been estimated using Rookley's Method on a dataset of
order book snapshots from Deribit, the leading BTC options market.
Bootstrap-based confidence bands have been estimated in order to
validate the results.

We assess the presence of well-established stylized facts of volatility
in the BTC market. We find horizontal dependence of volatility, meaning
that volatility tends to cluster and revert to the mean. The difference
between implied and realized volatility, commonly referred to as the
volatility premium, is substantial. Realized volatility rarely exceeds
the implied volatility. The IV term structure is found to be
traditional. Despite market participant's easy access to leverage, we
cannot confirm the existence of a leverage effect.

Our analysis extends the literature to a new asset class and contributes
to the pricing kernel puzzle. We are able to replicate empirical results
from the analysis of PKs in traditional markets, which are highly
correlated with aggregate wealth. Their similarity to PKs estimated from
BTC options indicates that BTC is becoming an established asset class.

Furthermore, our analysis sheds light on the BTC valuation and
risk-aversion of the retail traders. BTC option traders mostly consist
of retailers who are heterogeneous in their risk profile. The price of
short-dated instruments includes a high risk premium. Such instruments
reflect the anticipation of jumps in the underlying. These instruments
would be traded by either very risk-averse or risk-affine traders.
Long-dated instruments are employed as classic hedging instruments.
While a substantial risk premium is paid by traders in order to insure
themselves against falling prices, they are additionally (but to a
lesser degree) insuring themselves against sharply rising prices. Thus
investors are also hedging their risk of being priced out of a dynamic
market.

Several extensions of the presented research are available for the
future. Among those, we would find an extended dataset insightful, that
could support estimation of PKs and their evolution over a longer time
frame and possibly describe the convergence to the PKs of established
markets. It would also be interesting to analyze the evolution of PKs
around stress events in order to get further insights into investor risk
aversion, anticipation of such events and trading opportunities.

>>>>

\title{Empirical Option Returns and the risk-free Rate in Crypto Asset Markets}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{7 January 2024}

@@

We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness. We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., severe overpricings of at-the-money options. The effect holds after compensating for market crash insurance and transaction cost. 
We assess the deadweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.

@@

- scrape 8h funding rate continuously and use as market-interest rate

- scrape all BTC, ETH transactions from Deribit 
- load data, clean
- center on settlement date for each day (10am UTC)
- for each option, find the pendant via put-call-parity
- calculate the beta of each put, call
- build zero-beta straddles by finding weights such that the sum of weights is zero
- assess empirical, daily returns of the straddle
- build boxplots over levels of moneyness
- KDE --> t-distribution
- perform t-test for population mean of 0

@@

\section{Results}

We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
The null hypothesis is not rejected for all models, vanilla and crash-resistant, for ITM and OTM options. Conversely, the null hypothesis is firmly rejected on a high significance level for ATM options. 
Therefore, we accept the alternative hypothesis of an underperformance for ATM options. Consequently, we find a similar result to Shumway and Bakshi - that is the existence of a premium for ATM contracts. 
We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets - we figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk. 
Furthermore, there are mostly retailers present in the crypto option market. Some professional liquidity providers exist, but they remain few and therefore another reason for the premium's size could be illiquidity.

- the premium is larger when tau is small.

@@

Further research: 
- Evidence for leverage effect

%\begin{minipage}{\textwidth}
%    \centering
  %  \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
    %\captionof{figure}{Performance - Vanilla - No Fees}
    %\centering
    %\includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
     %\captionof{figure}{Performance - Vanilla - Fees}

%\end{minipage}
%\begin{minipage}{\textwidth}
%    \centering
%    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
%    \captionof{figure}{Performance - Crash Resistant - No Fees}
 %   \centering
 %   \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
 %    \captionof{figure}{Performance - Crash Resistant - Fees}

%\end{minipage}
   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}

%\label{ATM Term Structure}
%\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
\resizebox{\textwidth}{!}{\begin{tabular}{lllll}
  Moneyness    & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\

@@

@@

@@
